---
title: "Team info"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Team_info}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SpatialAssessmentModelingWorkshop)
```

| Group name | Model/Software | Point of Contact (& email) | Group participants | Confirmed participation (Y/N) | Group timeline |
|:----------:|:------------:|:-----------:|:----------:|:------------:|:-----------:|
| Team SS - IOTC | SS3 | Massimiliano Cardinale (massimiliano.cardinale@slu.se) | Massimiliano Cardinale (SLU), Rick Methot (NOAA), Dan Fu (IOTC), et al. | Y | ? |
| Team SS - ICES | SS3 | Maria Grazia Pennino (grazia.pennino@ieo.es)| Maria Grazia Pennino (IEO), Francisco Izquierdo (IEO), Santiago Cerviño (IEO), Marta Cousido (IEO), Giancarlo Correa (OSU) | Y | October 2021 - ... |
| Team SS - IATTC | SS3*VAST | Mark Maunder (mmaunder@iattc.org) | Mark Maunder (IATTC), Haikun Xu (IATTC), Carolina Minte-Vera (IATTC) | Y | August 2021 - ... |
| Team Recap-conditioned | Recapture-conditioned Model | Richard McGarvey (Richard.McGarvey@sa.gov.au) | Richard McGarvey (SARDI), John Feenestra (SARDI) | Y | ? |
| Team CASAL2 | CASAL2 | Craig Marsh (craig.marsh10@gmail.com) | Craig Marsh (University of Aukland/NIWA), Teresa A'Mar (NIWA), Arnaud Gruss (NIWA) | Y | August 2021 - ...|
| Team StPM | StPM (Cao et al)| Jie Cao / Maxime Olmos (jcao22@ncsu.edu / maxime.olmos@noaa.gov) | Jie Cao (NCSU), Maxime Olmos (UW/NOAA) | Y | ? |
| Team SPASAM | SPASAM | John Deroba (johnathan.deroba@noaa.gov) | John Deroba (NOAA-NEFSC), Brian Langseth (NOAA-NWFSC), et al | Y | ? | 
| Team MAS | MAS | Matthew Supernaw (matthew.supernaw@noaa.gov) | Matthew Supernaw (NOAA-OST), Jon Brodziak (NOAA-PIFSC) | Y | ? |
| Team MFCL | MFCL | Nicholas Ducharme-Barthe (nicholasd@spc.int) | Nicholas Ducharme-Barthe (SPC), John Hampton (SPC), Matt Vincent (NOAA-SEFSC), et al. | Y | October 2021-March 2022 |
