---
title: "Team info"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Team_info}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SpatialAssessmentModelingWorkshop)
```

|  Point of Contact (& email) | Model/Software | Group participants | Confirmed participation (Y/N) | Group timeline | Approach |
|:----------:|:------------:|:-----------:|:----------:|:------------:|:-----------:|
| Massimiliano Cardinale (massimiliano.cardinale@slu.se) | SS3 | Massimiliano Cardinale (SLU), Rick Methot (NOAA), Dan Fu (IOTC), Kathryn Doering (Caelum/NOAA-NWFSC), Agurtzane Urtizberea (AZTI), et al. | Y | ? | |
| Maria Grazia Pennino (grazia.pennino@ieo.es) | SS3 | Maria Grazia Pennino (IEO), Francisco Izquierdo (IEO), Santiago Cerviño (IEO), Marta Cousido (IEO), Giancarlo Correa (OSU) | Y | October 2021 - ... | |
| Mark Maunder (mmaunder@iattc.org) | SS3*VAST | Mark Maunder (IATTC), Haikun Xu (IATTC), Carolina Minte-Vera (IATTC) | Y | August 2021 - ... | |
| Richard McGarvey (Richard.McGarvey@sa.gov.au) | Recapture-conditioned Model | Richard McGarvey (SARDI), John Feenestra (SARDI) | Y | ? |
|  Craig Marsh (craig.marsh@niwa.co.nz) | CASAL2 | Craig Marsh (University of Aukland/NIWA), Teresa A'Mar (NIWA), Arnaud Gruss (NIWA) | Y | August 2021 - March 2022 | |
| Jie Cao / Maxime Olmos (jcao22@ncsu.edu / maxime.olmos@noaa.gov) | StPM (Cao et al) | Jie Cao (NCSU), Maxime Olmos (UW/NOAA) | Y | ? | |
| Jon Deroba (jonathan.deroba@noaa.gov) | SPASAM | Jon Deroba (NOAA-NEFSC), Brian Langseth (NOAA-NWFSC), Amy Schueller (NOAA-SEFSC), Dana Hanselman (NOAA-AFSC) | Y | September 2021 - Jan/Feb 2022 | |
| Matthew Supernaw (matthew.supernaw@noaa.gov) | MAS | Matthew Supernaw (NOAA-OST), Jon Brodziak (NOAA-PIFSC) | Y | ? | |
| Nicholas Ducharme-Barthe (nicholas.ducharme-barth@noaa.gov) | MFCL | Nicholas Ducharme-Barthe (NOAA-PIFSC), John Hampton (SPC), Matt Vincent (NOAA-SEFSC), Paul Hamer (SPC) | Y | October 2021-March 2022 | |
| Bjarki Elvarsson (bjarki.elvarsson@hafogvatn.is) | GADGET | Bjarki Elvarson (HI), Will Butler (HI), Alfonso Perez Rodriguez (IMR), Valerio Bartolino (SLU) | Y | October 2021 - ... | |
